---
title: "Distances_On_Data_05_01_25"
output: pdf_document
date: "2025-01-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cluster)
library(MASS)
library(arules)
library(aricode)
library(knitr)
library(kmed)
library(lsa)
library(nomclust)
library(UBL)
library(stats)
library(datasets)
library(manydist)
library(R6)
library(FactoMineR)
set.seed(2025)
```

## mtcars data
- 7 numerical variables
- 3 categorical variables
- 2 clusters (0:automatic, 1:manual)

```{r mtcars preprocess}
cars_df <- mtcars[,-9]
cars_clus <- mtcars[,9]
# make categorical columns factors instead of numeric
for (x in 8) {
   cars_df[,x] <- factor(cars_df[,x])
}

cars_df[,c(1,3:7)] <- scale(cars_df[,c(1,3:7)])

cars_num_df = cars_df
for (x in c(1:ncol(cars_num_df))){
  cars_num_df[,x] <- as.numeric(cars_num_df[,x])
}
```

```{r mtcars cluster, echo=FALSE}
ubdep_dist_cars <- mdist(cars_df)
eucl_dist_cars <- dist(cars_num_df, method="euclidean")
gower_dist_cars <- daisy(cars_df, metric="gower", type=list(asymm=8))
cos_dist_cars <- 1 - cosine(t(cars_num_df))
HVDM_dist_cars <- distances(1, cars_df, 'HVDM')
#ahm_dist_cars <- distmix(cars_df, method = 'ahmad', 
#                         idnum=c(1:7, 9:10), idbin=c(8))

ubdep_pam_cars <- pam(ubdep_dist_cars, 2, diss=TRUE)
eucl_pam_cars <- pam(eucl_dist_cars, 2, diss=TRUE)
gower_pam_cars <- pam(gower_dist_cars, 2, diss=TRUE)
cos_pam_cars <- pam(cos_dist_cars, 2, diss=TRUE)
HVDM_pam_cars <- pam(HVDM_dist_cars, 2, diss=TRUE)
#ahm_pam_cars <- pam(ahm_dist_cars, 2, diss=TRUE)

ubdep_clus_pam_cars <- ubdep_pam_cars$clustering
eucl_clus_pam_cars <- eucl_pam_cars$clustering
gower_clus_pam_cars <- gower_pam_cars$clustering
cos_clus_pam_cars <- cos_pam_cars$clustering
HVDM_clus_pam_cars <- HVDM_pam_cars$clustering
#ahm_clus_pam_cars <- ahm_pam_cars$clustering

ubdep_ari_pam_cars <- ARI(cars_clus, ubdep_clus_pam_cars)
eucl_ari_pam_cars <- ARI(cars_clus, eucl_clus_pam_cars)
gower_ari_pam_cars <- ARI(cars_clus, gower_clus_pam_cars)
cos_ari_pam_cars <- ARI(cars_clus, cos_clus_pam_cars)
HVDM_ari_pam_cars <- ARI(cars_clus, HVDM_clus_pam_cars)
#ahm_ari_pam_cars <- ARI(cars_clus, ahm_clus_pam_cars)

ubdep_ami_pam_cars <- AMI(cars_clus, ubdep_clus_pam_cars)
eucl_ami_pam_cars <- AMI(cars_clus, eucl_clus_pam_cars)
gower_ami_pam_cars <- AMI(cars_clus, gower_clus_pam_cars)
cos_ami_pam_cars <- AMI(cars_clus, cos_clus_pam_cars)
HVDM_ami_pam_cars <- AMI(cars_clus, HVDM_clus_pam_cars)
#ahm_ami_pam_cars <- AMI(cars_clus, ahm_clus_pam_cars)

ubdep_sil_pam_cars <- silhouette(ubdep_clus_pam_cars, ubdep_dist_cars)
eucl_sil_pam_cars <- silhouette(eucl_clus_pam_cars, eucl_dist_cars)
gower_sil_pam_cars <- silhouette(gower_clus_pam_cars, gower_dist_cars)
cos_sil_pam_cars <- silhouette(cos_clus_pam_cars, cos_dist_cars)
HVDM_sil_pam_cars <- silhouette(HVDM_clus_pam_cars, HVDM_dist_cars)
#ahm_sil_pam_cars <- silhouette(ahm_clus_pam_cars, ahm_dist_cars)

ubdep_sil_avg_pam_cars <- mean(ubdep_sil_pam_cars[,3])
eucl_sil_avg_pam_cars <- mean(eucl_sil_pam_cars[,3])
gower_sil_avg_pam_cars <- mean(gower_sil_pam_cars[,3])
cos_sil_avg_pam_cars <- mean(cos_sil_pam_cars[,3])
HVDM_sil_avg_pam_cars <- mean(HVDM_sil_pam_cars[,3])
#ahm_sil_avg_pam_cars <- mean(ahm_sil_pam_cars[,3])
```

```{r mtcars clustering stats}
dist_names_cars <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM')
cars_ari_pam <- c(ubdep_ari_pam_cars, eucl_ari_pam_cars, gower_ari_pam_cars, cos_ari_pam_cars, HVDM_ari_pam_cars)
cars_ami_pam <- c(ubdep_ami_pam_cars, eucl_ami_pam_cars, gower_ami_pam_cars, cos_ami_pam_cars, HVDM_ami_pam_cars)
cars_avg_sil_pam <- c(ubdep_sil_avg_pam_cars, eucl_sil_avg_pam_cars, gower_sil_avg_pam_cars, cos_sil_avg_pam_cars, HVDM_sil_avg_pam_cars)

scores_pam_cars <- data.frame(cars_ari_pam, cars_ami_pam, cars_avg_sil_pam, row.names = dist_names_cars)
colnames(scores_pam_cars) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_pam_cars, caption = "Statistics on mtcars Data with pam")
```


## cleveland heart data
- 5 numerical variables
- 8 categorical variables
- 2 clusters (0,1)

```{r cleveland heart data preprocess}
heart_data <- read.csv('data/heart.csv')
heart_df <- heart_data[,-14]
heart_clus <- heart_data[,14]
for (x in c(2:3,6:7,9,11:13)) {
   heart_df[,x] <- factor(heart_df[,x])
}
```

```{r cleveland heart data cluster, echo=FALSE}
ubdep_dist_heart <- mdist(heart_df)
eucl_dist_heart <- dist(heart_df, method="euclidean")
gower_dist_heart <- daisy(heart_df, metric="gower", 
                          type=list(asymm=c(2,6,9), factor=c(3,7,11:13)))
cos_dist_heart <- 1 - cosine(t(heart_data[,-14]))
HVDM_dist_heart <- distances(1, heart_df, 'HVDM')
ahm_dist_heart <- distmix(heart_df, method = 'ahmad', 
                         idnum=c(1, 4:5, 8,10), idbin=c(2,6,9), idcat=c(3,7,11:13))


ubdep_pam_heart <- pam(ubdep_dist_heart, 2, diss=TRUE)
eucl_pam_heart <- pam(eucl_dist_heart, 2, diss=TRUE)
gower_pam_heart <- pam(gower_dist_heart, 2, diss=TRUE)
cos_pam_heart <- pam(cos_dist_heart, 2, diss=TRUE)
HVDM_pam_heart <- pam(HVDM_dist_heart, 2, diss=TRUE)
ahm_pam_heart <- pam(ahm_dist_heart, 2, diss=TRUE)

ubdep_clus_pam_heart <- ubdep_pam_heart$clustering
eucl_clus_pam_heart <- eucl_pam_heart$clustering
gower_clus_pam_heart <- gower_pam_heart$clustering
cos_clus_pam_heart <- cos_pam_heart$clustering
HVDM_clus_pam_heart <- HVDM_pam_heart$clustering
ahm_clus_pam_heart <- ahm_pam_heart$clustering

ubdep_ari_pam_heart <- ARI(heart_clus, ubdep_clus_pam_heart)
eucl_ari_pam_heart <- ARI(heart_clus, eucl_clus_pam_heart)
gower_ari_pam_heart <- ARI(heart_clus, gower_clus_pam_heart)
cos_ari_pam_heart <- ARI(heart_clus, cos_clus_pam_heart)
HVDM_ari_pam_heart <- ARI(heart_clus, HVDM_clus_pam_heart)
ahm_ari_pam_heart <- ARI(heart_clus, ahm_clus_pam_heart)

ubdep_ami_pam_heart <- AMI(heart_clus, ubdep_clus_pam_heart)
eucl_ami_pam_heart <- AMI(heart_clus, eucl_clus_pam_heart)
gower_ami_pam_heart <- AMI(heart_clus, gower_clus_pam_heart)
cos_ami_pam_heart <- AMI(heart_clus, cos_clus_pam_heart)
HVDM_ami_pam_heart <- AMI(heart_clus, HVDM_clus_pam_heart)
ahm_ami_pam_heart <- AMI(heart_clus, ahm_clus_pam_heart)

ubdep_sil_pam_heart <- silhouette(ubdep_clus_pam_heart, ubdep_dist_heart)
eucl_sil_pam_heart <- silhouette(eucl_clus_pam_heart, eucl_dist_heart)
gower_sil_pam_heart <- silhouette(gower_clus_pam_heart, gower_dist_heart)
cos_sil_pam_heart <- silhouette(cos_clus_pam_heart, cos_dist_heart)
HVDM_sil_pam_heart <- silhouette(HVDM_clus_pam_heart, HVDM_dist_heart)
ahm_sil_pam_heart <- silhouette(ahm_clus_pam_heart, ahm_dist_heart)

ubdep_sil_avg_pam_heart <- mean(ubdep_sil_pam_heart[,3])
eucl_sil_avg_pam_heart <- mean(eucl_sil_pam_heart[,3])
gower_sil_avg_pam_heart <- mean(gower_sil_pam_heart[,3])
cos_sil_avg_pam_heart <- mean(cos_sil_pam_heart[,3])
HVDM_sil_avg_pam_heart <- mean(HVDM_sil_pam_heart[,3])
ahm_sil_avg_pam_heart <- mean(ahm_sil_pam_heart[,3])

```


```{r cleveland heart data clustering stats}
dist_names_heart <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
heart_ari_pam <- c(ubdep_ari_pam_heart, eucl_ari_pam_heart, gower_ari_pam_heart, cos_ari_pam_heart, HVDM_ari_pam_heart, ahm_ari_pam_heart)
heart_ami_pam <- c(ubdep_ami_pam_heart, eucl_ami_pam_heart, gower_ami_pam_heart, cos_ami_pam_heart, HVDM_ami_pam_heart, ahm_ami_pam_heart)
heart_avg_sil_pam <- c(ubdep_sil_avg_pam_heart, eucl_sil_avg_pam_heart, gower_sil_avg_pam_heart, cos_sil_avg_pam_heart, HVDM_sil_avg_pam_heart, ahm_sil_avg_pam_heart)

scores_pam_heart <- data.frame(heart_ari_pam, heart_ami_pam, heart_avg_sil_pam, row.names = dist_names_heart)
colnames(scores_pam_heart) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_pam_heart, caption = "Statistics on Cleveland Heart Data with pam")
```


## banking data
- 6 numerical variables
- 10 categorical variables
- 2 clusters ('yes', 'no')

```{r banking data preprocess}
set.seed(2025)
bank_data <- read.csv('data/banking.csv', sep=";")
rand_bank = sample(nrow(bank_data), nrow(bank_data)%/%100)
bank_df <- bank_data[,-17][rand_bank,]
bank_clus <- bank_data[,17][rand_bank]

for (x in c(2:5, 7:11,16)) {
   bank_df[,x] <- factor(bank_df[,x])
}

bank_num_df = bank_df
for (x in c(1:ncol(bank_num_df))){
  bank_num_df[,x] <- as.numeric(bank_num_df[,x])
}
```

```{r banking data cluster, echo=FALSE}
ubdep_dist_bank <- mdist(bank_df)
eucl_dist_bank <- dist(bank_num_df, method="euclidean")
gower_dist_bank <- daisy(bank_df, metric="gower", 
                          type=list(asymm=c(5,7:8), factor=c(2:4,9:11,16)))
cos_dist_bank <- 1 - cosine(t(bank_num_df[,-14]))
HVDM_dist_bank <- distances(1, bank_df, 'HVDM')
ahm_dist_bank <- distmix(bank_df, method = 'ahmad', 
                         idnum=c(1,6,12:15), idbin=c(5,7:8), idcat=c(2:4,9:11,16))


ubdep_pam_bank <- pam(ubdep_dist_bank, 2, diss=TRUE)
eucl_pam_bank <- pam(eucl_dist_bank, 2, diss=TRUE)
gower_pam_bank <- pam(gower_dist_bank, 2, diss=TRUE)
cos_pam_bank <- pam(cos_dist_bank, 2, diss=TRUE)
HVDM_pam_bank <- pam(HVDM_dist_bank, 2, diss=TRUE)
ahm_pam_bank <- pam(ahm_dist_bank, 2, diss=TRUE)

ubdep_clus_pam_bank <- ubdep_pam_bank$clustering
eucl_clus_pam_bank <- eucl_pam_bank$clustering
gower_clus_pam_bank <- gower_pam_bank$clustering
cos_clus_pam_bank <- cos_pam_bank$clustering
HVDM_clus_pam_bank <- HVDM_pam_bank$clustering
ahm_clus_pam_bank <- ahm_pam_bank$clustering

ubdep_ari_pam_bank <- ARI(bank_clus, ubdep_clus_pam_bank)
eucl_ari_pam_bank <- ARI(bank_clus, eucl_clus_pam_bank)
gower_ari_pam_bank <- ARI(bank_clus, gower_clus_pam_bank)
cos_ari_pam_bank <- ARI(bank_clus, cos_clus_pam_bank)
HVDM_ari_pam_bank <- ARI(bank_clus, HVDM_clus_pam_bank)
ahm_ari_pam_bank <- ARI(bank_clus, ahm_clus_pam_bank)

ubdep_ami_pam_bank <- AMI(bank_clus, ubdep_clus_pam_bank)
eucl_ami_pam_bank <- AMI(bank_clus, eucl_clus_pam_bank)
gower_ami_pam_bank <- AMI(bank_clus, gower_clus_pam_bank)
cos_ami_pam_bank <- AMI(bank_clus, cos_clus_pam_bank)
HVDM_ami_pam_bank <- AMI(bank_clus, HVDM_clus_pam_bank)
ahm_ami_pam_bank <- AMI(bank_clus, ahm_clus_pam_bank)

ubdep_sil_pam_bank <- silhouette(ubdep_clus_pam_bank, ubdep_dist_bank)
eucl_sil_pam_bank <- silhouette(eucl_clus_pam_bank, eucl_dist_bank)
gower_sil_pam_bank <- silhouette(gower_clus_pam_bank, gower_dist_bank)
cos_sil_pam_bank <- silhouette(cos_clus_pam_bank, cos_dist_bank)
HVDM_sil_pam_bank <- silhouette(HVDM_clus_pam_bank, HVDM_dist_bank)
ahm_sil_pam_bank <- silhouette(ahm_clus_pam_bank, ahm_dist_bank)

ubdep_sil_avg_pam_bank <- mean(ubdep_sil_pam_bank[,3])
eucl_sil_avg_pam_bank <- mean(eucl_sil_pam_bank[,3])
gower_sil_avg_pam_bank <- mean(gower_sil_pam_bank[,3])
cos_sil_avg_pam_bank <- mean(cos_sil_pam_bank[,3])
HVDM_sil_avg_pam_bank <- mean(HVDM_sil_pam_bank[,3])
ahm_sil_avg_pam_bank <- mean(ahm_sil_pam_bank[,3])

```

```{r banking data clustering stats}
dist_names_bank <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
bank_ari_pam <- c(ubdep_ari_pam_bank, eucl_ari_pam_bank, gower_ari_pam_bank, cos_ari_pam_bank, HVDM_ari_pam_bank, ahm_ari_pam_bank)
bank_ami_pam <- c(ubdep_ami_pam_bank, eucl_ami_pam_bank, gower_ami_pam_bank, cos_ami_pam_bank, HVDM_ami_pam_bank, ahm_ami_pam_bank)
bank_avg_sil_pam <- c(ubdep_sil_avg_pam_bank, eucl_sil_avg_pam_bank, gower_sil_avg_pam_bank, cos_sil_avg_pam_bank, HVDM_sil_avg_pam_bank, ahm_sil_avg_pam_bank)

scores_pam_bank <- data.frame(bank_ari_pam, bank_ami_pam, bank_avg_sil_pam, row.names = dist_names_bank)
colnames(scores_pam_bank) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_pam_bank, caption = "Statistics on Banking Data")
```


## customer segmentation data
- 3 numerical variables
- 6 categorical variables
- 4 clusters (A,B,C,D)

```{r customer segmentation data preprocess}
set.seed(2025)
cust_data <- read.csv('data/customer_segmentation.csv', sep=",")
cust_data <- na.omit(cust_data)

cust_data <- cust_data[-c(which(cust_data$Ever_Married == "")),]
cust_data <- cust_data[-c(which(cust_data$Graduated == "")),]
cust_data <- cust_data[-c(which(cust_data$Profession == "")),]
cust_data <- cust_data[-c(which(cust_data$Var_1 == "")),]

rand_cust = sample(nrow(cust_data), nrow(cust_data)%/%20)
cust_df <- cust_data[,-c(1,11)][rand_cust,]
cust_clus <- cust_data[,11][rand_cust]

for (x in c(1:2,4:5,7,9)) {
   cust_df[,x] <- factor(cust_df[,x])
}

cust_num_df = cust_df
for (x in c(1:ncol(cust_num_df))){
  cust_num_df[,x] <- as.numeric(cust_num_df[,x])
}
```

```{r customer segmentation data cluster, echo=FALSE}
ubdep_dist_cust <- mdist(cust_df)
eucl_dist_cust <- dist(cust_num_df, method="euclidean")
gower_dist_cust <- daisy(cust_df, metric="gower", 
                          type=list(asymm=c(1:2,4), factor=c(5,7,9)))
cos_dist_cust <- 1 - cosine(t(cust_num_df))
HVDM_dist_cust <- distances(1, cust_df, 'HVDM')
ahm_dist_cust <- distmix(cust_df, method = 'ahmad', 
                         idnum=c(3,6,8), idbin=c(1:2,4), idcat=c(5,7,9))


ubdep_pam_cust <- pam(ubdep_dist_cust, 4, diss=TRUE)
eucl_pam_cust <- pam(eucl_dist_cust, 4, diss=TRUE)
gower_pam_cust <- pam(gower_dist_cust, 4, diss=TRUE)
cos_pam_cust <- pam(cos_dist_cust, 4, diss=TRUE)
HVDM_pam_cust <- pam(HVDM_dist_cust, 4, diss=TRUE)
ahm_pam_cust <- pam(ahm_dist_cust, 4, diss=TRUE)

ubdep_clus_pam_cust <- ubdep_pam_cust$clustering
eucl_clus_pam_cust <- eucl_pam_cust$clustering
gower_clus_pam_cust <- gower_pam_cust$clustering
cos_clus_pam_cust <- cos_pam_cust$clustering
HVDM_clus_pam_cust <- HVDM_pam_cust$clustering
ahm_clus_pam_cust <- ahm_pam_cust$clustering

ubdep_ari_pam_cust <- ARI(cust_clus, ubdep_clus_pam_cust)
eucl_ari_pam_cust <- ARI(cust_clus, eucl_clus_pam_cust)
gower_ari_pam_cust <- ARI(cust_clus, gower_clus_pam_cust)
cos_ari_pam_cust <- ARI(cust_clus, cos_clus_pam_cust)
HVDM_ari_pam_cust <- ARI(cust_clus, HVDM_clus_pam_cust)
ahm_ari_pam_cust <- ARI(cust_clus, ahm_clus_pam_cust)

ubdep_ami_pam_cust <- AMI(cust_clus, ubdep_clus_pam_cust)
eucl_ami_pam_cust <- AMI(cust_clus, eucl_clus_pam_cust)
gower_ami_pam_cust <- AMI(cust_clus, gower_clus_pam_cust)
cos_ami_pam_cust <- AMI(cust_clus, cos_clus_pam_cust)
HVDM_ami_pam_cust <- AMI(cust_clus, HVDM_clus_pam_cust)
ahm_ami_pam_cust <- AMI(cust_clus, ahm_clus_pam_cust)

ubdep_sil_pam_cust <- silhouette(ubdep_clus_pam_cust, ubdep_dist_cust)
eucl_sil_pam_cust <- silhouette(eucl_clus_pam_cust, eucl_dist_cust)
gower_sil_pam_cust <- silhouette(gower_clus_pam_cust, gower_dist_cust)
cos_sil_pam_cust <- silhouette(cos_clus_pam_cust, cos_dist_cust)
HVDM_sil_pam_cust <- silhouette(HVDM_clus_pam_cust, HVDM_dist_cust)
ahm_sil_pam_cust <- silhouette(ahm_clus_pam_cust, ahm_dist_cust)

ubdep_sil_avg_pam_cust <- mean(ubdep_sil_pam_cust[,3])
eucl_sil_avg_pam_cust <- mean(eucl_sil_pam_cust[,3])
gower_sil_avg_pam_cust <- mean(gower_sil_pam_cust[,3])
cos_sil_avg_pam_cust <- mean(cos_sil_pam_cust[,3])
HVDM_sil_avg_pam_cust <- mean(HVDM_sil_pam_cust[,3])
ahm_sil_avg_pam_cust <- mean(ahm_sil_pam_cust[,3])
```

```{r customer segmentation data clustering stats}
dist_names_cust <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
cust_ari_pam <- c(ubdep_ari_pam_cust, eucl_ari_pam_cust, gower_ari_pam_cust, cos_ari_pam_cust, HVDM_ari_pam_cust, ahm_ari_pam_cust)
cust_ami_pam <- c(ubdep_ami_pam_cust, eucl_ami_pam_cust, gower_ami_pam_cust, cos_ami_pam_cust, HVDM_ami_pam_cust, ahm_ami_pam_cust)
cust_avg_sil_pam <- c(ubdep_sil_avg_pam_cust, eucl_sil_avg_pam_cust, gower_sil_avg_pam_cust, cos_sil_avg_pam_cust, HVDM_sil_avg_pam_cust, ahm_sil_avg_pam_cust)

scores_pam_cust <- data.frame(cust_ari_pam, cust_ami_pam, cust_avg_sil_pam, row.names = dist_names_cust)
colnames(scores_pam_cust) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_pam_cust, caption = "Statistics on Customer Segmentation Data")
```


## breast cancer data
- 30 numerical variables
- 0 categorical variables
- 2 clusters (Malignant or Benign)

```{r breast cancer data preprocess}
breast_data <- read.csv('data/breast-cancer.csv')
breast_df <- breast_data[,-c(1:2)]
breast_clus <- breast_data[,2]
```

```{r breast cancer data cluster, echo=FALSE}
ubdep_dist_breast <- mdist(breast_df)
eucl_dist_breast <- dist(breast_df, method="euclidean")
gower_dist_breast <- daisy(breast_df, metric="gower")
cos_dist_breast <- 1 - cosine(t(breast_df))
HVDM_dist_breast <- distances(1, breast_df, 'HVDM')
# ahm_dist_breast <- distmix(breast_df, method = 'ahmad', idnum=c(1:30))


ubdep_pam_breast <- pam(ubdep_dist_breast, 2, diss=TRUE)
eucl_pam_breast <- pam(eucl_dist_breast, 2, diss=TRUE)
gower_pam_breast <- pam(gower_dist_breast, 2, diss=TRUE)
cos_pam_breast <- pam(cos_dist_breast, 2, diss=TRUE)
HVDM_pam_breast <- pam(HVDM_dist_breast, 2, diss=TRUE)
# ahm_pam_breast <- pam(ahm_dist_breast, 2, diss=TRUE)

ubdep_clus_pam_breast <- ubdep_pam_breast$clustering
eucl_clus_pam_breast <- eucl_pam_breast$clustering
gower_clus_pam_breast <- gower_pam_breast$clustering
cos_clus_pam_breast <- cos_pam_breast$clustering
HVDM_clus_pam_breast <- HVDM_pam_breast$clustering
# ahm_clus_pam_breast <- ahm_pam_breast$clustering

ubdep_ari_pam_breast <- ARI(breast_clus, ubdep_clus_pam_breast)
eucl_ari_pam_breast <- ARI(breast_clus, eucl_clus_pam_breast)
gower_ari_pam_breast <- ARI(breast_clus, gower_clus_pam_breast)
cos_ari_pam_breast <- ARI(breast_clus, cos_clus_pam_breast)
HVDM_ari_pam_breast <- ARI(breast_clus, HVDM_clus_pam_breast)
# ahm_ari_pam_breast <- ARI(breast_clus, ahm_clus_pam_breast)

ubdep_ami_pam_breast <- AMI(breast_clus, ubdep_clus_pam_breast)
eucl_ami_pam_breast <- AMI(breast_clus, eucl_clus_pam_breast)
gower_ami_pam_breast <- AMI(breast_clus, gower_clus_pam_breast)
cos_ami_pam_breast <- AMI(breast_clus, cos_clus_pam_breast)
HVDM_ami_pam_breast <- AMI(breast_clus, HVDM_clus_pam_breast)
# ahm_ami_pam_breast <- AMI(breast_clus, ahm_clus_pam_breast)

ubdep_sil_pam_breast <- silhouette(ubdep_clus_pam_breast, ubdep_dist_breast)
eucl_sil_pam_breast <- silhouette(eucl_clus_pam_breast, eucl_dist_breast)
gower_sil_pam_breast <- silhouette(gower_clus_pam_breast, gower_dist_breast)
cos_sil_pam_breast <- silhouette(cos_clus_pam_breast, cos_dist_breast)
HVDM_sil_pam_breast <- silhouette(HVDM_clus_pam_breast, HVDM_dist_breast)
# ahm_sil_pam_breast <- silhouette(ahm_clus_pam_breast, ahm_dist_breast)

ubdep_sil_avg_pam_breast <- mean(ubdep_sil_pam_breast[,3])
eucl_sil_avg_pam_breast <- mean(eucl_sil_pam_breast[,3])
gower_sil_avg_pam_breast <- mean(gower_sil_pam_breast[,3])
cos_sil_avg_pam_breast <- mean(cos_sil_pam_breast[,3])
HVDM_sil_avg_pam_breast <- mean(HVDM_sil_pam_breast[,3])
# ahm_sil_avg_pam_breast <- mean(ahm_sil_pam_breast[,3])
```

```{r breast data clustering stats}
dist_names_breast <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM')
breast_ari_pam <- c(ubdep_ari_pam_breast, eucl_ari_pam_breast, gower_ari_pam_breast, cos_ari_pam_breast, HVDM_ari_pam_breast)
breast_ami_pam <- c(ubdep_ami_pam_breast, eucl_ami_pam_breast, gower_ami_pam_breast, cos_ami_pam_breast, HVDM_ami_pam_breast)
breast_avg_sil_pam <- c(ubdep_sil_avg_pam_breast, eucl_sil_avg_pam_breast, gower_sil_avg_pam_breast, cos_sil_avg_pam_breast, HVDM_sil_avg_pam_breast)

scores_pam_breast <- data.frame(breast_ari_pam, breast_ami_pam, breast_avg_sil_pam, row.names = dist_names_breast)
colnames(scores_pam_breast) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_pam_breast, caption = "Statistics on Breast Cancer Data")
```


## mobile phone price data
- 14 numerical variables
- 6 categorical variables
- 4 clusters (0,1,2,3)

```{r phone price data preprocess}
phone_data <- read.csv('data/mobile_price.csv') 
rand_phone = sample(nrow(phone_data), nrow(phone_data)%/%10)
phone_df <- phone_data[,-21][rand_phone,]
phone_clus <- phone_data[,21][rand_phone]


for (x in c(2,4,6,18:20)) {
   phone_df[,x] <- factor(phone_df[,x])
}

phone_num_df = phone_df
for (x in c(1:ncol(phone_num_df))){
  phone_num_df[,x] <- as.numeric(phone_num_df[,x])
}
```

```{r phone price data cluster, echo=FALSE}
ubdep_dist_phone <- mdist(phone_df)
eucl_dist_phone <- dist(phone_num_df, method="euclidean")
gower_dist_phone <- daisy(phone_df, metric="gower", 
                          type=list(asymm=c(2,4,6,18:20)))
cos_dist_phone <- 1 - cosine(t(phone_num_df))
HVDM_dist_phone <- distances(1, phone_df, 'HVDM')
ahm_dist_phone <- distmix(phone_df, method = 'ahmad', 
                         idnum=c(1,3,5,7:17), idbin=c(2,4,6,18:20))


ubdep_pam_phone <- pam(ubdep_dist_phone, 4, diss=TRUE)
eucl_pam_phone <- pam(eucl_dist_phone, 4, diss=TRUE)
gower_pam_phone <- pam(gower_dist_phone, 4, diss=TRUE)
cos_pam_phone <- pam(cos_dist_phone, 4, diss=TRUE)
HVDM_pam_phone <- pam(HVDM_dist_phone, 4, diss=TRUE)
ahm_pam_phone <- pam(ahm_dist_phone, 4, diss=TRUE)

ubdep_clus_pam_phone <- ubdep_pam_phone$clustering
eucl_clus_pam_phone <- eucl_pam_phone$clustering
gower_clus_pam_phone <- gower_pam_phone$clustering
cos_clus_pam_phone <- cos_pam_phone$clustering
HVDM_clus_pam_phone <- HVDM_pam_phone$clustering
ahm_clus_pam_phone <- ahm_pam_phone$clustering

ubdep_ari_pam_phone <- ARI(phone_clus, ubdep_clus_pam_phone)
eucl_ari_pam_phone <- ARI(phone_clus, eucl_clus_pam_phone)
gower_ari_pam_phone <- ARI(phone_clus, gower_clus_pam_phone)
cos_ari_pam_phone <- ARI(phone_clus, cos_clus_pam_phone)
HVDM_ari_pam_phone <- ARI(phone_clus, HVDM_clus_pam_phone)
ahm_ari_pam_phone <- ARI(phone_clus, ahm_clus_pam_phone)

ubdep_ami_pam_phone <- AMI(phone_clus, ubdep_clus_pam_phone)
eucl_ami_pam_phone <- AMI(phone_clus, eucl_clus_pam_phone)
gower_ami_pam_phone <- AMI(phone_clus, gower_clus_pam_phone)
cos_ami_pam_phone <- AMI(phone_clus, cos_clus_pam_phone)
HVDM_ami_pam_phone <- AMI(phone_clus, HVDM_clus_pam_phone)
ahm_ami_pam_phone <- AMI(phone_clus, ahm_clus_pam_phone)

ubdep_sil_pam_phone <- silhouette(ubdep_clus_pam_phone, ubdep_dist_phone)
eucl_sil_pam_phone <- silhouette(eucl_clus_pam_phone, eucl_dist_phone)
gower_sil_pam_phone <- silhouette(gower_clus_pam_phone, gower_dist_phone)
cos_sil_pam_phone <- silhouette(cos_clus_pam_phone, cos_dist_phone)
HVDM_sil_pam_phone <- silhouette(HVDM_clus_pam_phone, HVDM_dist_phone)
ahm_sil_pam_phone <- silhouette(ahm_clus_pam_phone, ahm_dist_phone)

ubdep_sil_avg_pam_phone <- mean(ubdep_sil_pam_phone[,3])
eucl_sil_avg_pam_phone <- mean(eucl_sil_pam_phone[,3])
gower_sil_avg_pam_phone <- mean(gower_sil_pam_phone[,3])
cos_sil_avg_pam_phone <- mean(cos_sil_pam_phone[,3])
HVDM_sil_avg_pam_phone <- mean(HVDM_sil_pam_phone[,3])
ahm_sil_avg_pam_phone <- mean(ahm_sil_pam_phone[,3])
```

```{r phone price data clustering stats}
dist_names_phone <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
phone_ari_pam <- c(ubdep_ari_pam_phone, eucl_ari_pam_phone, gower_ari_pam_phone, cos_ari_pam_phone, HVDM_ari_pam_phone, ahm_ari_pam_phone)
phone_ami_pam <- c(ubdep_ami_pam_phone, eucl_ami_pam_phone, gower_ami_pam_phone, cos_ami_pam_phone, HVDM_ami_pam_phone, ahm_ami_pam_phone)
phone_avg_sil_pam <- c(ubdep_sil_avg_pam_phone, eucl_sil_avg_pam_phone, gower_sil_avg_pam_phone, cos_sil_avg_pam_phone, HVDM_sil_avg_pam_phone, ahm_sil_avg_pam_phone)

scores_pam_phone <- data.frame(phone_ari_pam, phone_ami_pam, phone_avg_sil_pam, row.names = dist_names_phone)
colnames(scores_pam_phone) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_pam_phone, caption = "Statistics on Phone Price Data")
```


```{r stats by distance, echo=FALSE}
ubdep_ari_pam <- c(ubdep_ari_pam_cars, ubdep_ari_pam_heart, ubdep_ari_pam_bank, ubdep_ari_pam_cust, ubdep_ari_pam_breast, ubdep_ari_pam_phone)
ubdep_ami_pam <- c(ubdep_ami_pam_cars, ubdep_ami_pam_heart, ubdep_ami_pam_bank, ubdep_ami_pam_cust, ubdep_ami_pam_breast, ubdep_ami_pam_phone)
ubdep_avg_sil_pam <- c(ubdep_sil_avg_pam_cars,ubdep_sil_avg_pam_heart, ubdep_sil_avg_pam_bank, ubdep_sil_avg_pam_cust, ubdep_sil_avg_pam_breast, ubdep_sil_avg_pam_phone)

eucl_ari_pam <- c(eucl_ari_pam_cars, eucl_ari_pam_heart, eucl_ari_pam_bank, eucl_ari_pam_cust, eucl_ari_pam_breast, eucl_ari_pam_phone)
eucl_ami_pam <- c(eucl_ami_pam_cars, eucl_ami_pam_heart, eucl_ami_pam_bank, eucl_ami_pam_cust, eucl_ami_pam_breast, eucl_ami_pam_phone)
eucl_avg_sil_pam <- c(eucl_sil_avg_pam_cars,eucl_sil_avg_pam_heart, eucl_sil_avg_pam_bank, eucl_sil_avg_pam_cust, eucl_sil_avg_pam_breast, eucl_sil_avg_pam_phone)

gower_ari_pam <- c(gower_ari_pam_cars, gower_ari_pam_heart, gower_ari_pam_bank, gower_ari_pam_cust, gower_ari_pam_breast, gower_ari_pam_phone)
gower_ami_pam <- c(gower_ami_pam_cars, gower_ami_pam_heart, gower_ami_pam_bank, gower_ami_pam_cust, gower_ami_pam_breast, gower_ami_pam_phone)
gower_avg_sil_pam <- c(gower_sil_avg_pam_cars,gower_sil_avg_pam_heart, gower_sil_avg_pam_bank, gower_sil_avg_pam_cust, gower_sil_avg_pam_breast, gower_sil_avg_pam_phone)

cos_ari_pam <- c(cos_ari_pam_cars, cos_ari_pam_heart, cos_ari_pam_bank, cos_ari_pam_cust, cos_ari_pam_breast, cos_ari_pam_phone)
cos_ami_pam <- c(cos_ami_pam_cars, cos_ami_pam_heart, cos_ami_pam_bank, cos_ami_pam_cust, cos_ami_pam_breast, cos_ami_pam_phone)
cos_avg_sil_pam <- c(cos_sil_avg_pam_cars,cos_sil_avg_pam_heart, cos_sil_avg_pam_bank, cos_sil_avg_pam_cust, cos_sil_avg_pam_breast, cos_sil_avg_pam_phone)

HVDM_ari_pam <- c(HVDM_ari_pam_cars, HVDM_ari_pam_heart, HVDM_ari_pam_bank, HVDM_ari_pam_cust, HVDM_ari_pam_breast, HVDM_ari_pam_phone)
HVDM_ami_pam <- c(HVDM_ami_pam_cars, HVDM_ami_pam_heart, HVDM_ami_pam_bank, HVDM_ami_pam_cust, HVDM_ami_pam_breast, HVDM_ami_pam_phone)
HVDM_avg_sil_pam <- c(HVDM_sil_avg_pam_cars,HVDM_sil_avg_pam_heart, HVDM_sil_avg_pam_bank, HVDM_sil_avg_pam_cust, HVDM_sil_avg_pam_breast, HVDM_sil_avg_pam_phone)

ahm_ari_pam <- c(ahm_ari_pam_heart, ahm_ari_pam_bank, ahm_ari_pam_cust, ahm_ari_pam_phone)
ahm_ami_pam <- c(ahm_ami_pam_heart, ahm_ami_pam_bank, ahm_ami_pam_cust, ahm_ami_pam_phone)
ahm_avg_sil_pam <- c(ahm_sil_avg_pam_heart, ahm_sil_avg_pam_bank, ahm_sil_avg_pam_cust, ahm_sil_avg_pam_phone)
```

```{r average stats}
dist_names_all <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
avg_ari_all_pam <- c(mean(ubdep_ari_pam), mean(eucl_ari_pam), mean(gower_ari_pam), mean(cos_ari_pam), mean(HVDM_ari_pam), mean(ahm_ari_pam))
avg_ami_all_pam <- c(mean(ubdep_ami_pam), mean(eucl_ami_pam), mean(gower_ami_pam), mean(cos_ami_pam), mean(HVDM_ami_pam), mean(ahm_ami_pam))
avg_sil_all_pam <- c(mean(ubdep_avg_sil_pam), mean(eucl_avg_sil_pam), mean(gower_avg_sil_pam), mean(cos_avg_sil_pam), mean(HVDM_avg_sil_pam), mean(ahm_avg_sil_pam))

std_ari_all_pam <- c(sd(ubdep_ari_pam), sd(eucl_ari_pam), sd(gower_ari_pam), sd(cos_ari_pam), sd(HVDM_ari_pam), sd(ahm_ari_pam))
std_ami_all_pam <- c(sd(ubdep_ami_pam), sd(eucl_ami_pam), sd(gower_ami_pam), sd(cos_ami_pam), sd(HVDM_ami_pam), sd(ahm_ami_pam))
std_sil_all_pam <- c(sd(ubdep_avg_sil_pam), sd(eucl_avg_sil_pam), sd(gower_avg_sil_pam), sd(cos_avg_sil_pam), sd(HVDM_avg_sil_pam), sd(ahm_avg_sil_pam))

scores_mean_all_pam <- data.frame(avg_ari_all_pam, avg_ami_all_pam, avg_sil_all_pam, row.names = dist_names_all)
colnames(scores_mean_all_pam) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_mean_all_pam, caption = "Average Statistics on All Datasets with pam")

scores_std_all_pam <- data.frame(std_ari_all_pam, std_ami_all_pam, std_sil_all_pam, row.names = dist_names_all)
colnames(scores_std_all_pam) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_std_all_pam, caption = "Standard Deviation of Statistics on All Datasets with pam")
```

# skm clustering

## mtcars data
- 7 numerical variables
- 3 categorical variables
- 2 clusters (0:automatic, 1:manual)


```{r mtcars cluster skm, echo=FALSE}
ubdep_skm_cars <- skm(ubdep_dist_cars, 2)
eucl_skm_cars <- skm(eucl_dist_cars, 2)
gower_skm_cars <- skm(gower_dist_cars, 2)
cos_skm_cars <- skm(cos_dist_cars, 2)
HVDM_skm_cars <- skm(HVDM_dist_cars, 2)
#ahm_skm_cars <- skm(ahm_dist_cars, 2)

ubdep_clus_skm_cars <- ubdep_skm_cars$cluster
eucl_clus_skm_cars <- eucl_skm_cars$cluster
gower_clus_skm_cars <- gower_skm_cars$cluster
cos_clus_skm_cars <- cos_skm_cars$cluster
HVDM_clus_skm_cars <- HVDM_skm_cars$cluster
#ahm_clus_skm_cars <- ahm_skm_cars$cluster

ubdep_ari_skm_cars <- ARI(cars_clus, ubdep_clus_skm_cars)
eucl_ari_skm_cars <- ARI(cars_clus, eucl_clus_skm_cars)
gower_ari_skm_cars <- ARI(cars_clus, gower_clus_skm_cars)
cos_ari_skm_cars <- ARI(cars_clus, cos_clus_skm_cars)
HVDM_ari_skm_cars <- ARI(cars_clus, HVDM_clus_skm_cars)
#ahm_ari_skm_cars <- ARI(cars_clus, ahm_clus_skm_cars)

ubdep_ami_skm_cars <- AMI(cars_clus, ubdep_clus_skm_cars)
eucl_ami_skm_cars <- AMI(cars_clus, eucl_clus_skm_cars)
gower_ami_skm_cars <- AMI(cars_clus, gower_clus_skm_cars)
cos_ami_skm_cars <- AMI(cars_clus, cos_clus_skm_cars)
HVDM_ami_skm_cars <- AMI(cars_clus, HVDM_clus_skm_cars)
#ahm_ami_skm_cars <- AMI(cars_clus, ahm_clus_skm_cars)

ubdep_sil_skm_cars <- silhouette(ubdep_clus_skm_cars, ubdep_dist_cars)
eucl_sil_skm_cars <- silhouette(eucl_clus_skm_cars, eucl_dist_cars)
gower_sil_skm_cars <- silhouette(gower_clus_skm_cars, gower_dist_cars)
cos_sil_skm_cars <- silhouette(cos_clus_skm_cars, cos_dist_cars)
HVDM_sil_skm_cars <- silhouette(HVDM_clus_skm_cars, HVDM_dist_cars)
#ahm_sil_skm_cars <- silhouette(ahm_clus_skm_cars, ahm_dist_cars)

ubdep_sil_avg_skm_cars <- mean(ubdep_sil_skm_cars[,3])
eucl_sil_avg_skm_cars <- mean(eucl_sil_skm_cars[,3])
gower_sil_avg_skm_cars <- mean(gower_sil_skm_cars[,3])
cos_sil_avg_skm_cars <- mean(cos_sil_skm_cars[,3])
HVDM_sil_avg_skm_cars <- mean(HVDM_sil_skm_cars[,3])
#ahm_sil_avg_skm_cars <- mean(ahm_sil_skm_cars[,3])
```

```{r mtcars cluster stats skm}
dist_names_cars <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM')
cars_ari_skm <- c(ubdep_ari_skm_cars, eucl_ari_skm_cars, gower_ari_skm_cars, cos_ari_skm_cars, HVDM_ari_skm_cars)
cars_ami_skm <- c(ubdep_ami_skm_cars, eucl_ami_skm_cars, gower_ami_skm_cars, cos_ami_skm_cars, HVDM_ami_skm_cars)
cars_avg_sil_skm <- c(ubdep_sil_avg_skm_cars, eucl_sil_avg_skm_cars, gower_sil_avg_skm_cars, cos_sil_avg_skm_cars, HVDM_sil_avg_skm_cars)

scores_skm_cars <- data.frame(cars_ari_skm, cars_ami_skm, cars_avg_sil_skm, row.names = dist_names_cars)
colnames(scores_skm_cars) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_skm_cars, caption = "Statistics on mtcars Data with skm")
```


## cleveland heart data
- 5 numerical variables
- 8 categorical variables
- 2 clusters (0,1)

```{r cleveland heart data cluster skm, echo=FALSE}
ubdep_skm_heart <- skm(ubdep_dist_heart, 2)
eucl_skm_heart <- skm(eucl_dist_heart, 2)
gower_skm_heart <- skm(gower_dist_heart, 2)
cos_skm_heart <- skm(cos_dist_heart, 2)
HVDM_skm_heart <- skm(HVDM_dist_heart, 2)
ahm_skm_heart <- skm(ahm_dist_heart, 2)

ubdep_clus_skm_heart <- ubdep_skm_heart$cluster
eucl_clus_skm_heart <- eucl_skm_heart$cluster
gower_clus_skm_heart <- gower_skm_heart$cluster
cos_clus_skm_heart <- cos_skm_heart$cluster
HVDM_clus_skm_heart <- HVDM_skm_heart$cluster
ahm_clus_skm_heart <- ahm_skm_heart$cluster

ubdep_ari_skm_heart <- ARI(heart_clus, ubdep_clus_skm_heart)
eucl_ari_skm_heart <- ARI(heart_clus, eucl_clus_skm_heart)
gower_ari_skm_heart <- ARI(heart_clus, gower_clus_skm_heart)
cos_ari_skm_heart <- ARI(heart_clus, cos_clus_skm_heart)
HVDM_ari_skm_heart <- ARI(heart_clus, HVDM_clus_skm_heart)
ahm_ari_skm_heart <- ARI(heart_clus, ahm_clus_skm_heart)

ubdep_ami_skm_heart <- AMI(heart_clus, ubdep_clus_skm_heart)
eucl_ami_skm_heart <- AMI(heart_clus, eucl_clus_skm_heart)
gower_ami_skm_heart <- AMI(heart_clus, gower_clus_skm_heart)
cos_ami_skm_heart <- AMI(heart_clus, cos_clus_skm_heart)
HVDM_ami_skm_heart <- AMI(heart_clus, HVDM_clus_skm_heart)
ahm_ami_skm_heart <- AMI(heart_clus, ahm_clus_skm_heart)

ubdep_sil_skm_heart <- silhouette(ubdep_clus_skm_heart, ubdep_dist_heart)
eucl_sil_skm_heart <- silhouette(eucl_clus_skm_heart, eucl_dist_heart)
gower_sil_skm_heart <- silhouette(gower_clus_skm_heart, gower_dist_heart)
cos_sil_skm_heart <- silhouette(cos_clus_skm_heart, cos_dist_heart)
HVDM_sil_skm_heart <- silhouette(HVDM_clus_skm_heart, HVDM_dist_heart)
ahm_sil_skm_heart <- silhouette(ahm_clus_skm_heart, ahm_dist_heart)

ubdep_sil_avg_skm_heart <- mean(ubdep_sil_skm_heart[,3])
eucl_sil_avg_skm_heart <- mean(eucl_sil_skm_heart[,3])
gower_sil_avg_skm_heart <- mean(gower_sil_skm_heart[,3])
cos_sil_avg_skm_heart <- mean(cos_sil_skm_heart[,3])
HVDM_sil_avg_skm_heart <- mean(HVDM_sil_skm_heart[,3])
ahm_sil_avg_skm_heart <- mean(ahm_sil_skm_heart[,3])

```


```{r cleveland heart data cluster stats skm}
dist_names_heart <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
heart_ari_skm <- c(ubdep_ari_skm_heart, eucl_ari_skm_heart, gower_ari_skm_heart, cos_ari_skm_heart, HVDM_ari_skm_heart, ahm_ari_skm_heart)
heart_ami_skm <- c(ubdep_ami_skm_heart, eucl_ami_skm_heart, gower_ami_skm_heart, cos_ami_skm_heart, HVDM_ami_skm_heart, ahm_ami_skm_heart)
heart_avg_sil_skm <- c(ubdep_sil_avg_skm_heart, eucl_sil_avg_skm_heart, gower_sil_avg_skm_heart, cos_sil_avg_skm_heart, HVDM_sil_avg_skm_heart, ahm_sil_avg_skm_heart)

scores_skm_heart <- data.frame(heart_ari_skm, heart_ami_skm, heart_avg_sil_skm, row.names = dist_names_heart)
colnames(scores_skm_heart) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_skm_heart, caption = "Statistics on Cleveland Heart Data with skm")
```


## banking data
- 6 numerical variables
- 10 categorical variables
- 2 clusters ('yes', 'no')

```{r banking data cluster skm, echo=FALSE}
ubdep_skm_bank <- skm(ubdep_dist_bank, 2)
eucl_skm_bank <- skm(eucl_dist_bank, 2)
gower_skm_bank <- skm(gower_dist_bank, 2)
cos_skm_bank <- skm(cos_dist_bank, 2)
HVDM_skm_bank <- skm(HVDM_dist_bank, 2)
ahm_skm_bank <- skm(ahm_dist_bank, 2)

ubdep_clus_skm_bank <- ubdep_skm_bank$cluster
eucl_clus_skm_bank <- eucl_skm_bank$cluster
gower_clus_skm_bank <- gower_skm_bank$cluster
cos_clus_skm_bank <- cos_skm_bank$cluster
HVDM_clus_skm_bank <- HVDM_skm_bank$cluster
ahm_clus_skm_bank <- ahm_skm_bank$cluster

ubdep_ari_skm_bank <- ARI(bank_clus, ubdep_clus_skm_bank)
eucl_ari_skm_bank <- ARI(bank_clus, eucl_clus_skm_bank)
gower_ari_skm_bank <- ARI(bank_clus, gower_clus_skm_bank)
cos_ari_skm_bank <- ARI(bank_clus, cos_clus_skm_bank)
HVDM_ari_skm_bank <- ARI(bank_clus, HVDM_clus_skm_bank)
ahm_ari_skm_bank <- ARI(bank_clus, ahm_clus_skm_bank)

ubdep_ami_skm_bank <- AMI(bank_clus, ubdep_clus_skm_bank)
eucl_ami_skm_bank <- AMI(bank_clus, eucl_clus_skm_bank)
gower_ami_skm_bank <- AMI(bank_clus, gower_clus_skm_bank)
cos_ami_skm_bank <- AMI(bank_clus, cos_clus_skm_bank)
HVDM_ami_skm_bank <- AMI(bank_clus, HVDM_clus_skm_bank)
ahm_ami_skm_bank <- AMI(bank_clus, ahm_clus_skm_bank)

ubdep_sil_skm_bank <- silhouette(ubdep_clus_skm_bank, ubdep_dist_bank)
eucl_sil_skm_bank <- silhouette(eucl_clus_skm_bank, eucl_dist_bank)
gower_sil_skm_bank <- silhouette(gower_clus_skm_bank, gower_dist_bank)
cos_sil_skm_bank <- silhouette(cos_clus_skm_bank, cos_dist_bank)
HVDM_sil_skm_bank <- silhouette(HVDM_clus_skm_bank, HVDM_dist_bank)
ahm_sil_skm_bank <- silhouette(ahm_clus_skm_bank, ahm_dist_bank)

ubdep_sil_avg_skm_bank <- mean(ubdep_sil_skm_bank[,3])
eucl_sil_avg_skm_bank <- mean(eucl_sil_skm_bank[,3])
gower_sil_avg_skm_bank <- mean(gower_sil_skm_bank[,3])
cos_sil_avg_skm_bank <- mean(cos_sil_skm_bank[,3])
HVDM_sil_avg_skm_bank <- mean(HVDM_sil_skm_bank[,3])
ahm_sil_avg_skm_bank <- mean(ahm_sil_skm_bank[,3])

```

```{r banking data cluster stats skm}
dist_names_bank <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
bank_ari_skm <- c(ubdep_ari_skm_bank, eucl_ari_skm_bank, gower_ari_skm_bank, cos_ari_skm_bank, HVDM_ari_skm_bank, ahm_ari_skm_bank)
bank_ami_skm <- c(ubdep_ami_skm_bank, eucl_ami_skm_bank, gower_ami_skm_bank, cos_ami_skm_bank, HVDM_ami_skm_bank, ahm_ami_skm_bank)
bank_avg_sil_skm <- c(ubdep_sil_avg_skm_bank, eucl_sil_avg_skm_bank, gower_sil_avg_skm_bank, cos_sil_avg_skm_bank, HVDM_sil_avg_skm_bank, ahm_sil_avg_skm_bank)

scores_skm_bank <- data.frame(bank_ari_skm, bank_ami_skm, bank_avg_sil_skm, row.names = dist_names_bank)
colnames(scores_skm_bank) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_skm_bank, caption = "Statistics on Banking Data")
```


## customer segmentation data
- 3 numerical variables
- 6 categorical variables
- 4 clusters (A,B,C,D)


```{r customer segmentation data cluster skm, echo=FALSE}
ubdep_skm_cust <- skm(ubdep_dist_cust, 4)
eucl_skm_cust <- skm(eucl_dist_cust, 4)
gower_skm_cust <- skm(gower_dist_cust, 4)
cos_skm_cust <- skm(cos_dist_cust, 4)
HVDM_skm_cust <- skm(HVDM_dist_cust, 4)
ahm_skm_cust <- skm(ahm_dist_cust, 4)

ubdep_clus_skm_cust <- ubdep_skm_cust$cluster
eucl_clus_skm_cust <- eucl_skm_cust$cluster
gower_clus_skm_cust <- gower_skm_cust$cluster
cos_clus_skm_cust <- cos_skm_cust$cluster
HVDM_clus_skm_cust <- HVDM_skm_cust$cluster
ahm_clus_skm_cust <- ahm_skm_cust$cluster

ubdep_ari_skm_cust <- ARI(cust_clus, ubdep_clus_skm_cust)
eucl_ari_skm_cust <- ARI(cust_clus, eucl_clus_skm_cust)
gower_ari_skm_cust <- ARI(cust_clus, gower_clus_skm_cust)
cos_ari_skm_cust <- ARI(cust_clus, cos_clus_skm_cust)
HVDM_ari_skm_cust <- ARI(cust_clus, HVDM_clus_skm_cust)
ahm_ari_skm_cust <- ARI(cust_clus, ahm_clus_skm_cust)

ubdep_ami_skm_cust <- AMI(cust_clus, ubdep_clus_skm_cust)
eucl_ami_skm_cust <- AMI(cust_clus, eucl_clus_skm_cust)
gower_ami_skm_cust <- AMI(cust_clus, gower_clus_skm_cust)
cos_ami_skm_cust <- AMI(cust_clus, cos_clus_skm_cust)
HVDM_ami_skm_cust <- AMI(cust_clus, HVDM_clus_skm_cust)
ahm_ami_skm_cust <- AMI(cust_clus, ahm_clus_skm_cust)

ubdep_sil_skm_cust <- silhouette(ubdep_clus_skm_cust, ubdep_dist_cust)
eucl_sil_skm_cust <- silhouette(eucl_clus_skm_cust, eucl_dist_cust)
gower_sil_skm_cust <- silhouette(gower_clus_skm_cust, gower_dist_cust)
cos_sil_skm_cust <- silhouette(cos_clus_skm_cust, cos_dist_cust)
HVDM_sil_skm_cust <- silhouette(HVDM_clus_skm_cust, HVDM_dist_cust)
ahm_sil_skm_cust <- silhouette(ahm_clus_skm_cust, ahm_dist_cust)

ubdep_sil_avg_skm_cust <- mean(ubdep_sil_skm_cust[,3])
eucl_sil_avg_skm_cust <- mean(eucl_sil_skm_cust[,3])
gower_sil_avg_skm_cust <- mean(gower_sil_skm_cust[,3])
cos_sil_avg_skm_cust <- mean(cos_sil_skm_cust[,3])
HVDM_sil_avg_skm_cust <- mean(HVDM_sil_skm_cust[,3])
ahm_sil_avg_skm_cust <- mean(ahm_sil_skm_cust[,3])
```

```{r customer segmentation data cluster stats skm}
dist_names_cust <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
cust_ari_skm <- c(ubdep_ari_skm_cust, eucl_ari_skm_cust, gower_ari_skm_cust, cos_ari_skm_cust, HVDM_ari_skm_cust, ahm_ari_skm_cust)
cust_ami_skm <- c(ubdep_ami_skm_cust, eucl_ami_skm_cust, gower_ami_skm_cust, cos_ami_skm_cust, HVDM_ami_skm_cust, ahm_ami_skm_cust)
cust_avg_sil_skm <- c(ubdep_sil_avg_skm_cust, eucl_sil_avg_skm_cust, gower_sil_avg_skm_cust, cos_sil_avg_skm_cust, HVDM_sil_avg_skm_cust, ahm_sil_avg_skm_cust)

scores_skm_cust <- data.frame(cust_ari_skm, cust_ami_skm, cust_avg_sil_skm, row.names = dist_names_cust)
colnames(scores_skm_cust) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_skm_cust, caption = "Statistics on Customer Segmentation Data")
```


## breast cancer data
- 30 numerical variables
- 0 categorical variables
- 2 clusters (Malignant or Benign)

```{r breast cancer data cluster skm, echo=FALSE}
ubdep_skm_breast <- skm(ubdep_dist_breast, 2)
eucl_skm_breast <- skm(eucl_dist_breast, 2)
gower_skm_breast <- skm(gower_dist_breast, 2)
cos_skm_breast <- skm(cos_dist_breast, 2)
HVDM_skm_breast <- skm(HVDM_dist_breast, 2)
# ahm_skm_breast <- skm(ahm_dist_breast, 2)

ubdep_clus_skm_breast <- ubdep_skm_breast$cluster
eucl_clus_skm_breast <- eucl_skm_breast$cluster
gower_clus_skm_breast <- gower_skm_breast$cluster
cos_clus_skm_breast <- cos_skm_breast$cluster
HVDM_clus_skm_breast <- HVDM_skm_breast$cluster
# ahm_clus_skm_breast <- ahm_skm_breast$cluster

ubdep_ari_skm_breast <- ARI(breast_clus, ubdep_clus_skm_breast)
eucl_ari_skm_breast <- ARI(breast_clus, eucl_clus_skm_breast)
gower_ari_skm_breast <- ARI(breast_clus, gower_clus_skm_breast)
cos_ari_skm_breast <- ARI(breast_clus, cos_clus_skm_breast)
HVDM_ari_skm_breast <- ARI(breast_clus, HVDM_clus_skm_breast)
# ahm_ari_skm_breast <- ARI(breast_clus, ahm_clus_skm_breast)

ubdep_ami_skm_breast <- AMI(breast_clus, ubdep_clus_skm_breast)
eucl_ami_skm_breast <- AMI(breast_clus, eucl_clus_skm_breast)
gower_ami_skm_breast <- AMI(breast_clus, gower_clus_skm_breast)
cos_ami_skm_breast <- AMI(breast_clus, cos_clus_skm_breast)
HVDM_ami_skm_breast <- AMI(breast_clus, HVDM_clus_skm_breast)
# ahm_ami_skm_breast <- AMI(breast_clus, ahm_clus_skm_breast)

ubdep_sil_skm_breast <- silhouette(ubdep_clus_skm_breast, ubdep_dist_breast)
eucl_sil_skm_breast <- silhouette(eucl_clus_skm_breast, eucl_dist_breast)
gower_sil_skm_breast <- silhouette(gower_clus_skm_breast, gower_dist_breast)
cos_sil_skm_breast <- silhouette(cos_clus_skm_breast, cos_dist_breast)
HVDM_sil_skm_breast <- silhouette(HVDM_clus_skm_breast, HVDM_dist_breast)
# ahm_sil_skm_breast <- silhouette(ahm_clus_skm_breast, ahm_dist_breast)

ubdep_sil_avg_skm_breast <- mean(ubdep_sil_skm_breast[,3])
eucl_sil_avg_skm_breast <- mean(eucl_sil_skm_breast[,3])
gower_sil_avg_skm_breast <- mean(gower_sil_skm_breast[,3])
cos_sil_avg_skm_breast <- mean(cos_sil_skm_breast[,3])
HVDM_sil_avg_skm_breast <- mean(HVDM_sil_skm_breast[,3])
# ahm_sil_avg_skm_breast <- mean(ahm_sil_skm_breast[,3])
```

```{r breast data cluster stats skm}
dist_names_breast <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM')
breast_ari_skm <- c(ubdep_ari_skm_breast, eucl_ari_skm_breast, gower_ari_skm_breast, cos_ari_skm_breast, HVDM_ari_skm_breast)
breast_ami_skm <- c(ubdep_ami_skm_breast, eucl_ami_skm_breast, gower_ami_skm_breast, cos_ami_skm_breast, HVDM_ami_skm_breast)
breast_avg_sil_skm <- c(ubdep_sil_avg_skm_breast, eucl_sil_avg_skm_breast, gower_sil_avg_skm_breast, cos_sil_avg_skm_breast, HVDM_sil_avg_skm_breast)

scores_skm_breast <- data.frame(breast_ari_skm, breast_ami_skm, breast_avg_sil_skm, row.names = dist_names_breast)
colnames(scores_skm_breast) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_skm_breast, caption = "Statistics on Breast Cancer Data")
```


## mobile phone price data
- 14 numerical variables
- 6 categorical variables
- 4 clusters (0,1,2,3)

```{r phone price data cluster skm, echo=FALSE}
ubdep_skm_phone <- skm(ubdep_dist_phone, 4)
eucl_skm_phone <- skm(eucl_dist_phone, 4)
gower_skm_phone <- skm(gower_dist_phone, 4)
cos_skm_phone <- skm(cos_dist_phone, 4)
HVDM_skm_phone <- skm(HVDM_dist_phone, 4)
ahm_skm_phone <- skm(ahm_dist_phone, 4)

ubdep_clus_skm_phone <- ubdep_skm_phone$cluster
eucl_clus_skm_phone <- eucl_skm_phone$cluster
gower_clus_skm_phone <- gower_skm_phone$cluster
cos_clus_skm_phone <- cos_skm_phone$cluster
HVDM_clus_skm_phone <- HVDM_skm_phone$cluster
ahm_clus_skm_phone <- ahm_skm_phone$cluster

ubdep_ari_skm_phone <- ARI(phone_clus, ubdep_clus_skm_phone)
eucl_ari_skm_phone <- ARI(phone_clus, eucl_clus_skm_phone)
gower_ari_skm_phone <- ARI(phone_clus, gower_clus_skm_phone)
cos_ari_skm_phone <- ARI(phone_clus, cos_clus_skm_phone)
HVDM_ari_skm_phone <- ARI(phone_clus, HVDM_clus_skm_phone)
ahm_ari_skm_phone <- ARI(phone_clus, ahm_clus_skm_phone)

ubdep_ami_skm_phone <- AMI(phone_clus, ubdep_clus_skm_phone)
eucl_ami_skm_phone <- AMI(phone_clus, eucl_clus_skm_phone)
gower_ami_skm_phone <- AMI(phone_clus, gower_clus_skm_phone)
cos_ami_skm_phone <- AMI(phone_clus, cos_clus_skm_phone)
HVDM_ami_skm_phone <- AMI(phone_clus, HVDM_clus_skm_phone)
ahm_ami_skm_phone <- AMI(phone_clus, ahm_clus_skm_phone)

ubdep_sil_skm_phone <- silhouette(ubdep_clus_skm_phone, ubdep_dist_phone)
eucl_sil_skm_phone <- silhouette(eucl_clus_skm_phone, eucl_dist_phone)
gower_sil_skm_phone <- silhouette(gower_clus_skm_phone, gower_dist_phone)
cos_sil_skm_phone <- silhouette(cos_clus_skm_phone, cos_dist_phone)
HVDM_sil_skm_phone <- silhouette(HVDM_clus_skm_phone, HVDM_dist_phone)
ahm_sil_skm_phone <- silhouette(ahm_clus_skm_phone, ahm_dist_phone)

ubdep_sil_avg_skm_phone <- mean(ubdep_sil_skm_phone[,3])
eucl_sil_avg_skm_phone <- mean(eucl_sil_skm_phone[,3])
gower_sil_avg_skm_phone <- mean(gower_sil_skm_phone[,3])
cos_sil_avg_skm_phone <- mean(cos_sil_skm_phone[,3])
HVDM_sil_avg_skm_phone <- mean(HVDM_sil_skm_phone[,3])
ahm_sil_avg_skm_phone <- mean(ahm_sil_skm_phone[,3])
```

```{r phone price data cluster stats skm}
dist_names_phone <- c('Unbiased Dependant', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
phone_ari_skm <- c(ubdep_ari_skm_phone, eucl_ari_skm_phone, gower_ari_skm_phone, cos_ari_skm_phone, HVDM_ari_skm_phone, ahm_ari_skm_phone)
phone_ami_skm <- c(ubdep_ami_skm_phone, eucl_ami_skm_phone, gower_ami_skm_phone, cos_ami_skm_phone, HVDM_ami_skm_phone, ahm_ami_skm_phone)
phone_avg_sil_skm <- c(ubdep_sil_avg_skm_phone, eucl_sil_avg_skm_phone, gower_sil_avg_skm_phone, cos_sil_avg_skm_phone, HVDM_sil_avg_skm_phone, ahm_sil_avg_skm_phone)

scores_skm_phone <- data.frame(phone_ari_skm, phone_ami_skm, phone_avg_sil_skm, row.names = dist_names_phone)
colnames(scores_skm_phone) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_skm_phone, caption = "Statistics on Phone Price Data")
```


```{r stats by distance skm, echo=FALSE}
ubdep_ari_skm <- c(ubdep_ari_skm_cars, ubdep_ari_skm_heart, ubdep_ari_skm_bank, ubdep_ari_skm_cust, ubdep_ari_skm_breast, ubdep_ari_skm_phone)
ubdep_ami_skm <- c(ubdep_ami_skm_cars, ubdep_ami_skm_heart, ubdep_ami_skm_bank, ubdep_ami_skm_cust, ubdep_ami_skm_breast, ubdep_ami_skm_phone)
ubdep_avg_sil_skm <- c(ubdep_sil_avg_skm_cars,ubdep_sil_avg_skm_heart, ubdep_sil_avg_skm_bank, ubdep_sil_avg_skm_cust, ubdep_sil_avg_skm_breast, ubdep_sil_avg_skm_phone)

eucl_ari_skm <- c(eucl_ari_skm_cars, eucl_ari_skm_heart, eucl_ari_skm_bank, eucl_ari_skm_cust, eucl_ari_skm_breast, eucl_ari_skm_phone)
eucl_ami_skm <- c(eucl_ami_skm_cars, eucl_ami_skm_heart, eucl_ami_skm_bank, eucl_ami_skm_cust, eucl_ami_skm_breast, eucl_ami_skm_phone)
eucl_avg_sil_skm <- c(eucl_sil_avg_skm_cars,eucl_sil_avg_skm_heart, eucl_sil_avg_skm_bank, eucl_sil_avg_skm_cust, eucl_sil_avg_skm_breast, eucl_sil_avg_skm_phone)

gower_ari_skm <- c(gower_ari_skm_cars, gower_ari_skm_heart, gower_ari_skm_bank, gower_ari_skm_cust, gower_ari_skm_breast, gower_ari_skm_phone)
gower_ami_skm <- c(gower_ami_skm_cars, gower_ami_skm_heart, gower_ami_skm_bank, gower_ami_skm_cust, gower_ami_skm_breast, gower_ami_skm_phone)
gower_avg_sil_skm <- c(gower_sil_avg_skm_cars,gower_sil_avg_skm_heart, gower_sil_avg_skm_bank, gower_sil_avg_skm_cust, gower_sil_avg_skm_breast, gower_sil_avg_skm_phone)

cos_ari_skm <- c(cos_ari_skm_cars, cos_ari_skm_heart, cos_ari_skm_bank, cos_ari_skm_cust, cos_ari_skm_breast, cos_ari_skm_phone)
cos_ami_skm <- c(cos_ami_skm_cars, cos_ami_skm_heart, cos_ami_skm_bank, cos_ami_skm_cust, cos_ami_skm_breast, cos_ami_skm_phone)
cos_avg_sil_skm <- c(cos_sil_avg_skm_cars,cos_sil_avg_skm_heart, cos_sil_avg_skm_bank, cos_sil_avg_skm_cust, cos_sil_avg_skm_breast, cos_sil_avg_skm_phone)

HVDM_ari_skm <- c(HVDM_ari_skm_cars, HVDM_ari_skm_heart, HVDM_ari_skm_bank, HVDM_ari_skm_cust, HVDM_ari_skm_breast, HVDM_ari_skm_phone)
HVDM_ami_skm <- c(HVDM_ami_skm_cars, HVDM_ami_skm_heart, HVDM_ami_skm_bank, HVDM_ami_skm_cust, HVDM_ami_skm_breast, HVDM_ami_skm_phone)
HVDM_avg_sil_skm <- c(HVDM_sil_avg_skm_cars,HVDM_sil_avg_skm_heart, HVDM_sil_avg_skm_bank, HVDM_sil_avg_skm_cust, HVDM_sil_avg_skm_breast, HVDM_sil_avg_skm_phone)

ahm_ari_skm <- c(ahm_ari_skm_heart, ahm_ari_skm_bank, ahm_ari_skm_cust, ahm_ari_skm_phone)
ahm_ami_skm <- c(ahm_ami_skm_heart, ahm_ami_skm_bank, ahm_ami_skm_cust, ahm_ami_skm_phone)
ahm_avg_sil_skm <- c(ahm_sil_avg_skm_heart, ahm_sil_avg_skm_bank, ahm_sil_avg_skm_cust, ahm_sil_avg_skm_phone)
```

```{r average stats skm}
dist_names_all <- c('Unbiased Dep', 'Euclidean', 'Gower', 'Cosine', 'HVDM', 'Ahmad & Dey')
avg_ari_all_skm <- c(mean(ubdep_ari_skm), mean(eucl_ari_skm), mean(gower_ari_skm), mean(cos_ari_skm), mean(HVDM_ari_skm), mean(ahm_ari_skm))
avg_ami_all_skm <- c(mean(ubdep_ami_skm), mean(eucl_ami_skm), mean(gower_ami_skm), mean(cos_ami_skm), mean(HVDM_ami_skm), mean(ahm_ami_skm))
avg_sil_all_skm <- c(mean(ubdep_avg_sil_skm), mean(eucl_avg_sil_skm), mean(gower_avg_sil_skm), mean(cos_avg_sil_skm), mean(HVDM_avg_sil_skm), mean(ahm_avg_sil_skm))

std_ari_all_skm <- c(sd(ubdep_ari_skm), sd(eucl_ari_skm), sd(gower_ari_skm), sd(cos_ari_skm), sd(HVDM_ari_skm), sd(ahm_ari_skm))
std_ami_all_skm <- c(sd(ubdep_ami_skm), sd(eucl_ami_skm), sd(gower_ami_skm), sd(cos_ami_skm), sd(HVDM_ami_skm), sd(ahm_ami_skm))
std_sil_all_skm <- c(sd(ubdep_avg_sil_skm), sd(eucl_avg_sil_skm), sd(gower_avg_sil_skm), sd(cos_avg_sil_skm), sd(HVDM_avg_sil_skm), sd(ahm_avg_sil_skm))

scores_mean_all_skm <- data.frame(avg_ari_all_skm, avg_ami_all_skm, avg_sil_all_skm, row.names = dist_names_all)
colnames(scores_mean_all_skm) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_mean_all_skm, caption = "Average Statistics on All Datasets with skm")

scores_std_all_skm <- data.frame(std_ari_all_skm, std_ami_all_skm, std_sil_all_skm, row.names = dist_names_all)
colnames(scores_std_all_skm) <- c('ARI', 'AMI', 'Average Silhouette Score')
kable(scores_std_all_skm, caption = "Standard Deviation of Statistics on All Datasets with skm")
```

```{r Error-bar plot: ari pam}
library(ggplot2)

# Create a data frame
pam_ari_df <- data.frame(
  Distance = factor(dist_names_all, levels = dist_names_all),
  MeanARI = avg_ari_all_pam,
  SD = std_ari_all_pam
)

# Create the ggplot
ggplot(pam_ari_df, aes(x = Distance, y = MeanARI)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = MeanARI - SD, ymax = MeanARI + SD), width = 0.2) +
  labs(
    title = "Error Bar Plot for ARI Measurements (PAM)",
    x = "Distance Metric",
    y = "Mean ARI +/- SD"
  )

```

```{r Error-bar plot: ami pam}
# Create a data frame
pam_ami_df <- data.frame(
  Distance = factor(dist_names_all, levels = dist_names_all),
  MeanAMI = avg_ami_all_pam,
  SD = std_ami_all_pam
)

# Create the ggplot
ggplot(pam_ami_df, aes(x = Distance, y = MeanAMI)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = MeanAMI - SD, ymax = MeanAMI + SD), width = 0.2) +
  labs(
    title = "Error Bar Plot for AMI Measurements (PAM)",
    x = "Distance Metric",
    y = "Mean AMI +/- SD"
  )

```

```{r Error-bar plot: sil pam}
# Create a data frame
pam_sil_df <- data.frame(
  Distance = factor(dist_names_all, levels = dist_names_all),
  MeanSIL = avg_sil_all_pam,
  SD = std_sil_all_pam
)

# Create the ggplot
ggplot(pam_sil_df, aes(x = Distance, y = MeanSIL)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = MeanSIL - SD, ymax = MeanSIL + SD), width = 0.2) +
  labs(
    title = "Error Bar Plot for Silhouette Measurements (PAM)",
    x = "Distance Metric",
    y = "Mean Silhouette +/- SD"
  )

```

```{r Error-bar plot: ari skm}
# Create a data frame
skm_ari_df <- data.frame(
  Distance = factor(dist_names_all, levels = dist_names_all),
  MeanARI = avg_ari_all_skm,
  SD = std_ari_all_skm
)

# Create the ggplot
ggplot(skm_ari_df, aes(x = Distance, y = MeanARI)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = MeanARI - SD, ymax = MeanARI + SD), width = 0.2) +
  labs(
    title = "Error Bar Plot for ARI Measurements (K-medoids)",
    x = "Distance Metric",
    y = "Mean ARI +/- SD"
  )

```

```{r Error-bar plot: ami skm}
# Create a data frame
skm_ami_df <- data.frame(
  Distance = factor(dist_names_all, levels = dist_names_all),
  MeanAMI = avg_ami_all_skm,
  SD = std_ami_all_skm
)

# Create the ggplot
ggplot(skm_ami_df, aes(x = Distance, y = MeanAMI)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = MeanAMI - SD, ymax = MeanAMI + SD), width = 0.2) +
  labs(
    title = "Error Bar Plot for AMI Measurements (K-medoids)",
    x = "Distance Metric",
    y = "Mean AMI +/- SD"
  )

```

```{r Error-bar plot: sil skm}
# Create a data frame
skm_sil_df <- data.frame(
  Distance = factor(dist_names_all, levels = dist_names_all),
  MeanSIL = avg_sil_all_skm,
  SD = std_sil_all_skm
)

# Create the ggplot
ggplot(skm_sil_df, aes(x = Distance, y = MeanSIL)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = MeanSIL - SD, ymax = MeanSIL + SD), width = 0.2) +
  labs(
    title = "Error Bar Plot for Silhouette Measurements (K-medoids)",
    x = "Distance Metric",
    y = "Mean Silhouette +/- SD"
  )

```



